Paper

### 2018-11-13 paper.Rmd
included relationship between poll div and nestedness and funct compl. also effect of div on fruit set and find interesting results!!!

f.agg$weighted_NODF<-out.site$weighted_NODF[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$int_evenness<-out.site$int_evenness[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$H2<-out.site$H2[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$functional.comp.poll<-out.site$functional.comp.poll[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$niche.overlap.plant<-out.site$niche.overlap.plant[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$modularity<-out.site$modularity[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$nodf.song<-out.site$nodf.song[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$link_dens<-out.site$link_dens[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$Shannon<-out.site$Shannon[match(f.agg$Site_ID, out.site$Site_id)]

@@

f.agg2<-na.omit(f.agg)
#cor(f.agg2[,c(5:10, 12:19)])

@@

```
#### Function as SEED NUMBER

@@

s.agg$weighted_NODF<-out.site$weighted_NODF[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$int_evenness<-out.site$int_evenness[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$H2<-out.site$H2[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$functional.comp.poll<-out.site$functional.comp.poll[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$niche.overlap.plant<-out.site$niche.overlap.plant[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$modularity<-out.site$modularity[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$nodf.song<-out.site$nodf.song[match(s.agg$Site_ID, out.site$Site_id)]

@@

pl2
# 
# interact_plot(m2.see, pred = "functional.comp.poll", modx = "nodf.song", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
#               modx.labels= c("Mean nestedness + 1 SD", "Mean nestedness", "Mean nestedness - 1 SD"))

@@

>>>>

f.agg$weighted_NODF<-out.site$weighted_NODF[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$int_evenness<-out.site$int_evenness[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$H2<-out.site$H2[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$functional.comp.poll<-out.site$functional.comp.poll[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$niche.overlap.plant<-out.site$niche.overlap.plant[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$modularity<-out.site$modularity[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$nodf.song<-out.site$nodf.song[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$link_dens<-out.site$link_dens[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$Shannon<-out.site$Shannon[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$species.poll<-out.site$species.poll[match(f.agg$Site_ID, out.site$Site_id)]
f.agg$species.pl<-out.site$species.pl[match(f.agg$Site_ID, out.site$Site_id)]

@@

f.agg2<-na.omit(f.agg)
#cor(f.agg2[,c(5:13, 15:24)])

@@

Relationship between pollinator diversity, nestedness and functinal comp. Less diverse communities have higher levels of nestedness, hence redundancy while more diverse comm have higher levels of complementarity. 
These variables are highly correlated so analyze separately. Communities with greater diversity of pollinators have less fruit set!! Opposite to BEF relationships!!! the negative effect of diversty on nestedness ends up having an effect on function! it would be interesting to see temporal dynamics here.

m1.fr.div<-glmmTMB(mean.fruitset ~ species.poll +  (1|Plant.sp), family="gaussian", data=f.agg2)
summary(m1.fr.div)

pl.div<-ggplot(f.agg2,  aes(x=species.poll, y=mean.fruitset, color=Plant.sp))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Pollinator species diversity") +      
        ylab("Mean fruitset") + theme_bw() +  theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold")) + labs(col="Plant species")

pl.div

m1.fr.pl.div<-glmmTMB(mean.fruitset ~ species.pl +  (1|Plant.sp), family="gaussian", data=f.agg2)
summary(m1.fr.pl.div)

#### Function as SEED NUMBER

@@

s.agg$weighted_NODF<-out.site$weighted_NODF[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$int_evenness<-out.site$int_evenness[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$H2<-out.site$H2[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$functional.comp.poll<-out.site$functional.comp.poll[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$niche.overlap.plant<-out.site$niche.overlap.plant[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$modularity<-out.site$modularity[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$nodf.song<-out.site$nodf.song[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$species.poll<-out.site$species.poll[match(s.agg$Site_ID, out.site$Site_id)]
s.agg$species.pl<-out.site$species.pl[match(s.agg$Site_ID, out.site$Site_id)]

@@

pl2
# 
# interact_plot(m2.see, pred = "nodf.song", modx = "species.poll", interval = TRUE, plot.points = TRUE, int.type = "confidence",  facet.modx = TRUE, x.label = "Functional complementarity", y.label = "Mean seed number/fruit",
#                modx.labels= c("Mean nestedness + 1 SD", "Mean nestedness", "Mean nestedness - 1 SD"))

@@

Relationship between pollinator diversity AND SEED SET

m1.seed.div<-glmmTMB( mean.seednumber ~ species.poll  +  (1|Plant.sp), family="poisson", data=s.agg4)
summary(m1.seed.div)

m1.seed.pl.div<-glmmTMB( mean.seednumber ~ species.pl  +  (1|Plant.sp), family="poisson", data=s.agg4)
summary(m1.seed.pl.div)

pl.div2<-ggplot(s.agg4,  aes(x=species.pl, y=mean.seednumber, color=Plant.sp))+      
        geom_point(size=4) + geom_smooth(method=lm, size=1.5, se=TRUE, color = "black", alpha=0.2) + 
        geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
        xlab("Plant species diversity") +      
        ylab("Mean number of seeds/fruit") + theme_bw() +  theme(text = element_text(size = 15), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1), face="bold")) + labs(col="Plant species")

pl.div2
